---
title: "Peernorms"
author: "Emmy Green"
date: "11/29/2018"
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(ggplot2)
library(dplyr)
library(forcats)
library(lme4)
library(devtools)
library(MASS)
library(nnet)
library(citr)
library(RefManageR)
library(survival)
library(survminer)
library(car)
library(brms)
library(plyr)
library(effects)
library(broom)
library(purrr)
library(car)
library(psych)
library(mediation)

```
#Calling the Data
```{r,include=FALSE}

#Call from choose
peernorms<-read.csv(file.choose())

```
#Cleaning Data
```{r, include=FALSE}

#Data frames

#Drop kids
peernorms<-peernorms%>% 
  filter(drop==0)

#Define age_exact as numeric variable
peernorms$age_exact<-as.numeric(peernorms$age_exact)

#Define gender as categorical variable
peernorms$gender <- as.factor(peernorms$gender)

#Define race as categorical variable
peernorms$racecode<-factor(peernorms$racecode, levels = c(0, 1))

#Relabel race cateogry labels
peernorms$racecode<-revalue(peernorms$racecode, c("0" = "White", "1" = "Minority"))

#Define condition as categorical
peernorms$condition <-factor(peernorms$condition, levels = c("0", "1"))

#Relabel condition labels
peernorms$condition <-revalue(peernorms$condition, c("0" = "control", "1" = "friendship"))

#Defining neighborhood as numeric 
peernorms$neighborhoodbg<-as.numeric(peernorms$neighborhoodbg)
peernorms$neighborhoodbb<-as.numeric(peernorms$neighborhoodbb)
peernorms$neighborhoodwg<-as.numeric(peernorms$neighborhoodwg)
peernorms$neighborhoodwb<-as.numeric(peernorms$neighborhoodwb)

# Creating composite variables

#Attitudes towards black target (rescaled to be 1-6; higher means positive about black)
peernorms<-peernorms%>%
  mutate(attitude_black = (likebg + likebb + nicebg + nicebb)/4)

#Attitudes towards White target (rescaled to be 1-6; higher means positive about white)
peernorms<-peernorms%>%
  mutate(attitude_white = (likewg + likewb + nicewg + nicewb)/4) 

#ProWhite bias (scale: -5 to 5; positive number means bias towards whites)
peernorms<-peernorms%>%
  mutate(pro_white_bias = (attitude_white - attitude_black))

#ProWhite bias - GENDER INGROUP (scale: -10 to 10; positive number means bias towards whites)
#peernorms<-peernorms%>%
 # mutate(prowhitebias_gingroup = ((likeingroupw + niceingroupw) - (likeingroupb + niceingroupb)))

#ProWhite bias - GENDER OUTGROUP (scale: -10 to 10; positive number means bias towards whites)
#peernorms<-peernorms%>%
  #mutate(prowhitebias_goutgroup = ((likeoutgroupw + niceoutgroupw) - (likeoutgroupb + niceoutgroupb)))

#Creating Neighborhood Diversity (scale: higher means more likely to see black than white)
peernorms<-peernorms%>%
  mutate(neighborhood = (neighborhoodbg + neighborhoodbb) - (neighborhoodwg + neighborhoodwb))

#Creating similar variable
peernorms<- peernorms%>%
  mutate(similar= (similarities1 + similarities2 + similarities3 + similarities4)/4)

#Creating the expectations for helpful behavior variable:
peernorms<- peernorms%>%
  mutate(expectations_helpful= (expectations_white + expectations_black)/2)

#Creating the peer norms variable:
peernorms<- peernorms%>%
  mutate(norms= (norms_white +norms_black)/2)

#Set Neighborhood Diveresity as numeric variable
peernorms$neighborhood<-as.numeric(peernorms$neighborhood)

#Centering age_exact 
peernorms<-peernorms%>%
  mutate(age_exactc = (age_exact - (mean(age_exact))))

#Centering Neighborhood Diversity
peernorms$neighborhoodc<-scale(peernorms$neighborhood,center=TRUE,scale=FALSE)

```
#Descriptive Analyses
```{r, include=FALSE}

# Frequencies 
N=xtabs(~ condition + racecode, peernorms)
N

mean(peernorms$age_exact)
SD(peernorms$age_exact)

#Descriptives
#Comparing means by condition

aggregate(peernorms$similar~peernorms$condition,FUN=mean)
aggregate(peernorms$attitude_black~peernorms$condition,FUN=mean)
aggregate(peernorms$expectations_friend~peernorms$condition,FUN=mean)
aggregate(peernorms$expectations_black~peernorms$condition,FUN=mean)
aggregate(peernorms$expectations_white~peernorms$condition,FUN=mean)
aggregate(peernorms$expectations_helpful~peernorms$condition,FUN=mean)
aggregate(peernorms$norms~peernorms$condition,FUN=mean)
aggregate(peernorms$you_friends~peernorms$condition,FUN=mean)

aggregate(peernorms$similar~peernorms$condition,FUN=SD)
aggregate(peernorms$attitude_black~peernorms$condition,FUN=SD)
aggregate(peernorms$expectations_friend~peernorms$condition,FUN=SD)
aggregate(peernorms$expectations_black~peernorms$condition,FUN=SD)
aggregate(peernorms$expectations_white~peernorms$condition,FUN=SD)
aggregate(peernorms$norms~peernorms$condition,FUN=SD)
aggregate(peernorms$expectations_helpful~peernorms$condition,FUN=SD)
aggregate(peernorms$you_friends~peernorms$condition,FUN=SD)

aggregate(cbind(peernorms$similar,peernorms$attitude_black,peernorms$expectations_friend) ~ peernorms$condition, FUN=mean) 
```
#Analyses
```{r, include = FALSE}
#Attitude toward black children

#Attitudes toward black children by participant race and age
attitudemod<-lm(attitude_black ~ racecode * age_exact, data = peernorms)
attitudemod_summary<-as.data.frame(coef(summary(attitudemod)))

summary (attitudemod)
#ANOVA
Anova(attitudemod)

##Figure0 attitudes

attitudesfigure0<-ggplot(peernorms, aes(x=age_exact, y=attitude_black, color = racecode)) +
  geom_jitter(shape = .25, width = .15, height = .15) +
  geom_smooth (method = "glm", alpha = .1) +
  ylim(0,7) +
  scale_color_manual(values = c("red", "blue", "purple"))+
  theme_bw() +
  labs(x="Age", y="Children's Attitudes Toward the Black Targets")

attitudesfigure0

meanattitude<-effect("racecode * age_exact",attitudemod)
meanattitude<-as.data.frame(meanattitude)
meanattitude

#Attitudes toward black children by race and condition (friendship or control)
attitudemod2<-lm(attitude_black~racecode * condition, data= peernorms)
attitudemod2_summary <-as.data.frame(coef(summary(attitudemod2)))

summary(attitudemod2)
#ANOVA
Anova(attitudemod2)

#Attitudes toward black children by race, condition (friendship or control) and age
attitudemod3<-lm(attitude_black~racecode * condition * age_exact, data= peernorms)
attitudemod3_summary <-as.data.frame(coef(summary(attitudemod3)))

summary(attitudemod3)

meanattitude3<-effect("racecode * condition * age_exact",attitudemod3)
meanattitude3<-as.data.frame(meanattitude3)
meanattitude3

#ANOVA
Anova(attitudemod3)

##Figure1 and figure2 attitudes
attitudesfigure1<-ggplot(peernorms, mapping = aes(x=racecode, y=attitude_black, fill = condition)) +
  geom_boxplot() + 
 geom_jitter(shape = .25) +
  ylim(1, 6) +
  scale_color_manual(values = c("red", "blue", "purple"))+
  theme_bw() +
  labs(x="Race", y="Children's Attitudes Towards the Black Targets")

attitudesfigure1

attitudesfigure2<-ggplot(peernorms, aes(x=age_exact, y=attitude_black, color = condition)) +
  facet_wrap(~racecode) +
  geom_jitter(shape = .25, width = .15, height = .15) +
  geom_smooth (method = "glm", alpha = .1) +
  ylim(0,7) +
  scale_color_manual(values = c("red", "blue", "purple"))+
  theme_bw() +
  labs(x="Age", y="Children's Attitudes Toward the Black Targets")

attitudesfigure2
```

```{r, include = FALSE}

#Attitude toward white children

#LM Attitude toward white children by race and age
attitudemodw<-lm(attitude_white ~ racecode * age_exact, data = peernorms)
attitudemodw_summary<-as.data.frame(coef(summary(attitudemodw)))

summary (attitudemodw)
#ANOVA
Anova(attitudemodw)

#Attitude toward white children by race and condition
attitudemodw2<-lm(attitude_white~racecode * condition, data= peernorms)
attitudemodw2_summary <-as.data.frame(coef(summary(attitudemodw2)))

summary(attitudemodw2)
#ANOVA
Anova(attitudemodw2)

#Attitude toward white children by race, condition and age
attitudemodw3<-lm(attitude_white~racecode * condition * age_exact, data= peernorms)
attitudemodw3_summary <-as.data.frame(coef(summary(attitudemodw3)))

summary(attitudemodw3)

meanattitudew3<-effect("condition * age_exact",attitudemodw3)
meanattitudew3<-as.data.frame(meanattitudew3)
meanattitudew3
```

```{r, include = FALSE}
#ProWhite Bias

#LM Pro White Bias
pro_white_mod<-lm(pro_white_bias ~ racecode * age_exact, data = peernorms)
pro_white_mod_summary<-as.data.frame(coef(summary(pro_white_mod)))

summary (pro_white_mod)

#ANOVA
Anova(pro_white_mod)

#Pro white and condition
pro_white_mod2<-lm(pro_white_bias ~racecode * condition, data = peernorms)
pro_white_mod2_summary<-as.data.frame(coef(summary(pro_white_mod2)))

summary(pro_white_mod2)

#Pro white and condition
pro_white_mod3<-lm(pro_white_bias ~racecode * condition * age_exact, data = peernorms)
pro_white_mod3_summary<-as.data.frame(coef(summary(pro_white_mod3)))

summary(pro_white_mod3)

##Figure pro white bias
#prowhitefigure<-ggplot(peernorms, mapping = aes(x=condition, y=attitude_white, fill = race)) +
  #geom(boxplot) + 
  #geom_jitter(shape = 1) +
  #ylim(1, 6) +
  #scale_color_manual(values = c("red", "blue", "purple"))+
 # theme_bw() +
  #labs(x="Condition", y="Children's Pro-White Bias")

#prowhitefigure
```

```{r, include = FALSE}
#expectations of friendship
expectations_friend_mod<- lm(expectations_friend ~racecode * condition * age_exact, data=peernorms)
expectations_friend_mod_summary<-as.data.frame(coef(summary(expectations_friend_mod)))
summary(expectations_friend_mod)

expectations_friend_mod2<- lm(expectations_friend ~condition, data=peernorms)
expectations_friend_mod2_summary<-as.data.frame(coef(summary(expectations_friend_mod2)))
summary(expectations_friend_mod2)

#expectations of helpful behavior
#expectations_white
expectations_white_mod<- lm(expectations_white ~racecode * condition * age_exact, data=peernorms)
expectations_white_mod_summary<-as.data.frame(coef(summary(expectations_white_mod)))
summary(expectations_white_mod)

expectations_white_mod2<- lm(expectations_white ~condition, data=peernorms)
expectations_white_mod2_summary<-as.data.frame(coef(summary(expectations_white_mod2)))
summary(expectations_white_mod2)

#expectations_black
expectations_black_mod<- lm(expectations_black ~racecode * condition * age_exact, data=peernorms)
expectations_black_mod_summary<-as.data.frame(coef(summary(expectations_black_mod)))
summary(expectations_black_mod)

expectations_black_mod2<- lm(expectations_black ~condition, data=peernorms)
expectations_black_mod2_summary<-as.data.frame(coef(summary(expectations_black_mod2)))
summary(expectations_black_mod2)

#expectations_helpful
expectations_helpful_mod<- lm(expectations_helpful~ racecode * condition * age_exact, data= peernorms)
expectations_helpful_summary<-as.data.frame(coef(summary(expectations_helpful_mod)))
summary(expectations_helpful_mod)

expectations_helpful_mod2<- lm(expectations_helpful~ condition, data= peernorms)
expectations_helpful_mod2_summary<-as.data.frame(coef(summary(expectations_helpful_mod2)))
summary(expectations_helpful_mod2)

#prepare data for repeated measures ANOVA  
expectations <- peernorms %>% gather(stim, resp, "expectations_black", "expectations_white")
expectations <- expectations %>% separate(stim, into = c("expectations_gen", "target_race"), sep=13)

expectations$target_race <- as.factor(expectations$target_race)

#repeated measures ANOVA
expec_anova<-aov(resp ~ target_race * racecode * condition * age_exact, data=expectations)
summary(expec_anova)

mean_expec_anova<-effect("condition * age_exact", expec_anova)
mean_expec_anova<-as.data.frame(mean_expec_anova)
mean_expec_anova

```

```{r, include = FALSE}
#similarity

#composite similar variable
similar_mod <- lm(similar ~ racecode * condition * age_exact, data=peernorms)
similar_mod_summary<-as.data.frame(coef(summary(similar_mod)))
summary(similar_mod)

similar_mod2 <- lm(similar ~ condition, data=peernorms)
similar_mod2_summary<-as.data.frame(coef(summary(similar_mod2)))
summary(similar_mod2)

#individual similarity items

similarities_mod1 <- lm(similarities1 ~racecode * condition * age_exact, data=peernorms)
similarities_mod1_summary<-as.data.frame(coef(summary(similarities_mod1)))
summary(similarities_mod1)

mean_similarities1<-effect("age_exact", similarities_mod1)
mean_similarities1<-as.data.frame(mean_similarities1)
mean_similarities1

similarities_mod2 <- lm(similarities2 ~racecode * condition * age_exact, data=peernorms)
similarities_mod2_summary<-as.data.frame(coef(summary(similarities_mod2)))
summary(similarities_mod2)

similarities_mod3 <- lm(similarities3 ~racecode * condition * age_exact, data=peernorms)
similarities_mod3_summary<-as.data.frame(coef(summary(similarities_mod3)))
summary(similarities_mod3)

similarities_mod4 <- lm(similarities4 ~racecode * condition * age_exact, data=peernorms)
similarities_mod4_summary<-as.data.frame(coef(summary(similarities_mod4)))
summary(similarities_mod4)
```

```{r, include = FALSE}
#norms

#norms_white
norms_white_mod <- lm(norms_white ~ racecode * condition * age_exact, data=peernorms)
norms_white_mod_summary<-as.data.frame(coef(summary(norms_white_mod)))
summary(norms_white_mod)

norms_white_mod2 <- lm(norms_white ~ condition, data=peernorms)
norms_white_mod2_summary<-as.data.frame(coef(summary(norms_white_mod2)))
summary(norms_white_mod2)

#norms_black
norms_black_mod <- lm(norms_black ~ racecode * condition * age_exact, data=peernorms)
norms_black_mod_summary<-as.data.frame(coef(summary(norms_black_mod)))
summary(norms_black_mod)

norms_black_mod2 <- lm(norms_black ~ condition, data=peernorms)
norms_black_mod2_summary<-as.data.frame(coef(summary(norms_black_mod2)))
summary(norms_black_mod2)

#prepare data for repeated measures ANOVA  
norms <- peernorms %>% gather(stim, resp, "norms_black", "norms_white")
norms <- norms %>% separate(stim, into = c("norms_gen", "target_race"), sep=6)

norms$target_race <- as.factor(norms$target_race)

#repeated measures ANOVA for individual norms items
norms_anova<-aov(resp ~ target_race * racecode * condition * age_exact, data=norms)
summary(norms_anova)

mean_norms_anova<-effect("racecode * condition", norms_anova)
mean_norms_anova<-as.data.frame(mean_norms_anova)
mean_norms_anova

#norms composite 
norms_mod <- lm(norms ~racecode * condition * age_exact, data=peernorms)
norms_mod_summary<-as.data.frame(coef(summary(norms_mod)))
summary(norms_mod)

norms_mod2 <- lm(norms ~condition, data=peernorms)
norms_mod2_summary<-as.data.frame(coef(summary(norms_mod2)))
summary(norms_mod2)

#you_friends
norms_you_mod<- lm(you_friends ~ condition * racecode, data=peernorms)
norms_you_mod_summary<-as.data.frame(coef(summary(norms_you_mod)))
summary(norms_you_mod)

norms_you_mod2<- lm(you_friends ~ condition, data=peernorms)
norms_you_mod2_summary<-as.data.frame(coef(summary(norms_you_mod2)))
summary(norms_you_mod2)

mean_you<-effect("condition * racecode", norms_you_mod)
mean_you<-as.data.frame(mean_you)
mean_you

#you_friends figure
you_friends_figure<-ggplot(peernorms, mapping = aes(x=racecode, y=you_friends, fill = condition)) +
  geom_boxplot() + 
 geom_jitter(shape = .25) +
  ylim(1, 6) +
  scale_color_manual(values = c("red", "blue", "purple"))+
  theme_bw() +
  labs(x="Race", y="Do you want these kids to be friends?")

you_friends_figure

#Correlations
cor.test(peernorms$attitude_black,peernorms$similar, method= "pearson", exact=FALSE) #p=7.902e-05
cor.test(peernorms$attitude_black,peernorms$norms, method= "pearson", exact=FALSE)  #p= 7.305e-05
cor.test(peernorms$attitude_black,peernorms$expectations_helpful, method= "pearson", exact=FALSE) # p=.008
cor.test(peernorms$attitude_black,peernorms$expectations_friend, method= "pearson", exact=FALSE) # p= .018
cor.test(peernorms$attitude_black,peernorms$you_friends, method= "pearson", exact=FALSE) #p=1.795e-05
```

```{r, include = FALSE}
#Mediation analyses 

#Expectations of friendship as a mediator 

peernorms<-peernorms
na.omit(peernorms,cols=c(“condition”,“expectations_friend”,“attitude_black”))

sem1<- “# a path
expectations_friend ~ a*condition  #mediator as a function of IV

 #b path
attitude_black ~ b*expectations_friend  #DV as a function of mediator

 #c’path
attitude_black ~ cp*condition  #c-prime path aka DV as function of IV

 ab := a*b
 total := cp + ab”

set.seed(1234)

sem1<-sem(sem1,data=peernorms,se=“bootstrap”,bootstrap = 1000)
summary(sem1,standardized=TRUE)

#Expectations of helpful behavior as a mediator 

peernorms<-peernorms
na.omit(peernorms,cols=c(“condition”,“expectations_helpful”,“attitude_black”))

sem2<- “# a path
expectations_helpful ~ a*condition  #mediator as a function of IV

 #b path
attitude_black ~ b*expectations_helpful  #DV as a function of mediator

 #c’path
attitude_black ~ cp*condition  #c-prime path aka DV as function of IV

 ab := a*b
 total := cp + ab”

set.seed(1234)

sem2<-sem(sem1,data=peernorms,se=“bootstrap”,bootstrap = 1000)
summary(sem1,standardized=TRUE)

#Expectations of perceived similarity as a mediator 

peernorms<-peernorms
na.omit(peernorms,cols=c(“condition”,“similar”,“attitude_black”))

sem3<- “# a path
similar ~ a*condition  #mediator as a function of IV

 #b path
attitude_black ~ b*similar  #DV as a function of mediator

 #c’path
attitude_black ~ cp*condition  #c-prime path aka DV as function of IV

 ab := a*b
 total := cp + ab”

set.seed(1234)

sem3<-sem(sem1,data=peernorms,se=“bootstrap”,bootstrap = 1000)
summary(sem1,standardized=TRUE)

#Expectations of peer norms as a mediator 

peernorms<-peernorms
na.omit(peernorms,cols=c(“condition”,“norms”,“attitude_black”))

sem4<- “# a path
norms~ a*condition  #mediator as a function of IV

 #b path
attitude_black ~ b*norms  #DV as a function of mediator

 #c’path
attitude_black ~ cp*condition  #c-prime path aka DV as function of IV

 ab := a*b
 total := cp + ab”

set.seed(1234)

sem4<-sem(sem1,data=peernorms,se=“bootstrap”,bootstrap = 1000)
summary(sem1,standardized=TRUE)